\documentclass[a4paper,11pt]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}

% Page setup
\geometry{margin=2.5cm}

% Title info
\title{Assignment 3: Machine Learning for Time Series}
\author{Frederik Appel Vardinghus-Nielsen}
\date{\today}

\begin{document}

\maketitle
\listoftodos

\section{FD001: Single Condition, Single Fault Mode}

\subsection{Problem understanding}
The RUL task is a regression problem since the target variable is a time period. The variable in this task is in a unit of cycles, which are strictly discrete, but there are no predefined classed and the range has no upper bound, so regression is more fitting.

One row in the dataset represents one cycle, the unit of time. Each row contains info on engine value, operation settings, time and sensor values.

RUL labels must be constructed from the given failure time in cycle number.
\begin{itemize}
\item The train series run until failure, so the labels will be the total number of cycles minus the current cycle number.
\item The test series do not unr until failure but the number of cycles until failure wheh the series ends is given so the labels will be the length of the test series plus the RUL at the end of the series minus the the current cycle number.
\end{itemize}

\subsection{Exploratory data analysis}
The sensor channels were chosen based upon their Spearman correlation with the cycle number. The Spearman correlation was calculated individually for each sensor for each engine and then aggregated across engines by mean. The sensor channels with mean Spearman correlation above 0.5 and standard deviation below 0.3 were selected. This results in 12 sensors.

\subsection{Data preparation}
\begin{itemize}
\item \textbf{RUL label contruction:} constructed as piecewise-linear with a cap of 125 cycles. RUL beyond 125 is not expected to show sensor values that are much different from other healthy data points, so capping prevents the model from attempting to learn less relevant patterns and focus of the part where health deterioration is more evident.
\item \textbf{Train/validation split:} A classic 80/20 split by engines for train/val is used.
\item \textbf{Normalization:} The sensor values are normalized by subtracting the mean and dividing by the standard deviation of each sensor channel across engines in the training set.
\item \textbf{Fixed random seed:} A fixed random seed (42) for the train/validation split is used to ensure reproducibility.
\end{itemize}
\subsection{Feature engineering -- raw fixed-window pipeline}
A window length $w=30$ is used and treated as hyperparameter in the later tuning task.

\subsection{Feature engineering-- feature-sequence pipeline}
The feature sequence pipeline is based on the raw fixed-window pipeline but with additional feature engineering. For each window, the following suggested features are calculated for each sensor channel:
\begin{itemize}
    \item Rolling mean
    \item Rolling standard deviation
    \item Linear OLS slope
    \item Rolling mean deviation from baseline (first window) value
\end{itemize}

To handle variable-length sequences for the feature approach the pack\_padded\_sequence and pad\_packed\_sequence functions from PyTorch are used. The MSE loss is masked to ignore the padded values.

\subsection{Models}
The three models RNN, LSTM and TCN are configured with the default suggestions:
\begin{itemize}
    \item RNN/LSTM: two recurrent layers of size 128; dropout of 0.2 after first layer.
    \item TCN: 4 dilated residual blocks with output dimension = 64; dilation $\in\{1,2,4,8\}$; fully connected head.
    \item ADAM optimiser: learning rate = 0.001
    \item MSE loss
    \item Epochs: max 200; early stopping patience = 10.
    \item Batch size: 64
\end{itemize}

\subsection{XGBoost baseline}
XGBoost is tuned with Optuna (TPE sampler, 100 trials) minimising validation RMSE.
The searched hyperparameters and their ranges are listed in Table~\ref{tab:xgb_hparams}.

\begin{table}[h]
    \centering
    \begin{tabular}{llll}
        \hline
        \textbf{Parameter} & \textbf{Range} & \textbf{Scale} & \textbf{Type} \\
        \hline
        \texttt{learning\_rate}     & $[0.001,\ 0.3]$  & log     & continuous \\
        \texttt{max\_depth}         & $[3,\ 10]$       & uniform & integer    \\
        \texttt{subsample}          & $[0.5,\ 1.0]$    & uniform & continuous \\
        \texttt{colsample\_bytree}  & $[0.5,\ 1.0]$    & uniform & continuous \\
        \texttt{min\_child\_weight} & $[1,\ 20]$       & uniform & integer    \\
        \texttt{reg\_lambda}        & $[0.01,\ 10.0]$  & log     & continuous \\
        \hline
    \end{tabular}
    \caption{Optuna hyperparameter search space for XGBoost. \texttt{n\_estimators} is fixed at 1000 and controlled by early stopping (patience = 30 rounds).}
    \label{tab:xgb_hparams}
\end{table}

\section{Evaluation protocol}

\subsection{Metrics}
NASA score is not used for training loss.

\subsection{Multiple seeds}
Five fixed random seeds (42, 123, 456, 789, 1011) are used for model initialization when training to probe the model sensitivity to initial conditions. The mean and standard deviation of the RMSE and NASA scores across seeds for each model and data approach can be seen in Table~\ref{tab:multi_seed_results}.

\begin{table}[h]
    \centering
    \begin{tabular}{llrrrr}
        \hline
        \textbf{Approach} & \textbf{Model} & \textbf{RMSE mean} & \textbf{RMSE std} & \textbf{NASA mean} & \textbf{NASA std} \\
        \hline
        window   & RNN     & -- & -- & -- & -- \\
        window   & LSTM    & -- & -- & -- & -- \\
        window   & TCN     & -- & -- & -- & -- \\
        sequence & RNN     & -- & -- & -- & -- \\
        sequence & LSTM    & -- & -- & -- & -- \\
        sequence & TCN     & -- & -- & -- & -- \\
        sequence & XGBoost & -- & -- & -- & -- \\
        \hline
    \end{tabular}
    \caption{Mean and standard deviation of RMSE and NASA score across five seeds per model and data approach on FD001 test set.}
    \label{tab:multi_seed_results}
\end{table}

\subsection{Fair comparison}
No deviations from the suggested setup made.

\section{Focused hyperparameter study}

\subsection{Setup}

\subsection{Analysis}



\end{document}